SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-15 docs/questioning.tex
minor changes

There is already a survey on mitigating software vulnerabilities in
general~\cite{SZ12}. The scope of that research is much broader than
ours and leaves out the majority of the approaches and mechanisms that
we consider in this work. This is mainly because that work includes
countermeasures that identify vulnerabilities using program analysis
(which takes place during the development or testing phases), while we
consider protection mechanisms that counter web attacks when they take
place. Similarly, static or dynamic analysis techniques that examine
applications to identify vulnerabilities that may lead to the attacks
that we described earlier are out of scope as well. While
countermeasures against {\sc sql} injection attacks have been
previously surveyed in a 2006 paper~\cite{HVO06}, a significant number
of new {\sc sql} injection defenses has been proposed since then, as
we mentioned earlier.

@@

A policy enforcement technique developed by Mozilla,
called {\sc csp} (Content Security Policy)~\cite{cspMoz,SSM10}
is currently supported by many browsers to detect
{\sc xss} and {\sc csrf} attacks. To eliminate such
attacks, web site administrators
can specify which domains the browser should treat
as valid sources of script and which not. Then, the browser
(Point {\sc ub}) will only execute scripts that exist in
source files from white-listed domains.

>>>>

There is already a survey on mitigating software vulnerabilities in
general~\cite{SZ12}. The scope of that research is much broader than
ours and leaves out the majority of the approaches and mechanisms that
we consider in this work. This is mainly because that work includes
countermeasures that identify vulnerabilities using static program analysis
(which takes place during the development or testing phases), while we
consider protection mechanisms that counter web attacks when they take
place. Similarly, dynamic analysis techniques that examine
applications to identify vulnerabilities that may lead to the attacks
that we described earlier are out of scope as well. While
countermeasures against {\sc sql} injection attacks have been
previously surveyed in a 2006 paper~\cite{HVO06}, a significant number
of new {\sc sql} injection defenses has been proposed since then, as
we mentioned earlier.

@@

A policy enforcement technique developed by Mozilla,
called {\sc csp} (Content Security Policy)~\cite{cspMoz,SSM10}
is currently supported by many browsers to prevent
{\sc xss} and {\sc csrf} attacks. To eliminate such
attacks, web site administrators
can specify which domains the browser should treat
as valid sources of script and which not. Then, the browser
(Point {\sc ub}) will only execute scripts that exist in
source files from white-listed domains.
